Modeling defoliation as a proxy for tree health: A case study on Pinus Radiata trees using machine-learning and hyperspectral data

### 2018-08-07 01_writing/Schratz_hyperspectral.tex
write conclusion

\noindent The algorithms were benchmarked in two ways:
1) Using spatial block \ac{CV} on the plot level with each plot serving as the test set once.
This approach results in four performance estimates, one for each fold.
2) Using five-fold five-times repeated spatial \ac{CV} for each plot based on the k-means clustering approach of \cite{sperrorest}.
As the best algorithm of 1) will be used for the spatial prediction, we first conducted the model selection on this setup and only applied the winning algorithm on 2).

% Add figure visualizing both spCV approaches

@@

% Performance estimates
\begin{table}[t!]
\centering
\caption[t]{Four-fold block spatial \ac{CV} performances of RR, SVM and xgboost using \ac{RMSE} as the error measure.
	Mean and standard deviation are shown.}
\begingroup\footnotesize
\begin{tabular}{llll}
	RR            & SVM           & xgboost       & xgboost (7 variables) \\
	\hline
	59.10 (22.71) & 36.23 (15.73) & 33.26 (16.61) &                       \\
	\bottomrule
\end{tabular}
\endgroup
\label{tab:model_comparison}
\end{table}

@@

\noindent The spatial predictions showed that the model tries to avoid making extreme predictions since most values ranged between 30 \% and 80 \%. 
This behavior is mainly triggered by the conentration of the model on the distribution of defoliation in the \textit{Laukiz 1}, \textit{Luiando} and \textit{Oiartzun} training plots.
This focus then causes the high prediction error for \textit{Laukiz 2} for which a lot of defoliation values actually range between 0 \% and 20 \%.
The fitted model would need more training samples for plots that show a similar defoliation as \textit{Laukiz 2} to reach a better performance for similar plots.

@@

>>>>

\noindent The algorithms were benchmarked in two ways:
1) Using spatial block \ac{CV} on the plot level with each plot serving as the test set once.
This approach results in four performance estimates, one for each fold.
2) Using five-fold five-times repeated spatial \ac{CV} for each plot based on the k-means clustering approach of \cite{sperrorest} (\autoref{fig:spcv}).
As the best algorithm of 1) will be used for the spatial prediction, we first conducted the model selection on this setup and only applied the winning algorithm on 2).

% defoliation boxplots
\begin{figure} [b!]
	\begin{center}
		\makebox[\textwidth]{\includegraphics[width=1\textwidth] {spcv_folds_demon_plots.pdf}}
		\caption{Fold 1 of the spatial partitioning using k-means clustering for \textit{Laukiz 1}, \textit{Laukiz 2}, \textit{Luiando} and \textit{Oiartzun}.}
		\label{fig:spcv}
	\end{center}
\end{figure}

@@

% Performance estimates
\begin{table}[t!]
\centering
\caption[t]{Four-fold block spatial \ac{CV} performances of RR, SVM and xgboost using \ac{RMSE} as the error measure.
	Mean and standard deviation are shown.}
\begingroup\footnotesize
\begin{tabular}{llll}
	RR            & SVM           & xgboost       & xgboost (7 variables) \\
	\hline
	59.10 (22.71) & 36.23 (15.73) & 33.26 (16.61) & 29.59   (16.09)              \\
	\bottomrule
\end{tabular}
\endgroup
\label{tab:model_comparison}
\end{table}

@@

\noindent The spatial predictions showed that the model tries to avoid making extreme predictions since most values ranged between 30 \% and 80 \%.
This behavior is mainly triggered by the concentration of the model on the distribution of defoliation in the \textit{Laukiz 1}, \textit{Luiando} and \textit{Oiartzun} training plots.
This focus then causes the high prediction error for \textit{Laukiz 2} for which a lot of defoliation values actually range between 0 \% and 20 \%.
The fitted model would need more training samples for plots that show a similar defoliation as \textit{Laukiz 2} to reach a better performance for similar plots.

@@

\noindent In this work we used various indices derived from hyperspectral remote sensing data to estimate defoliation in northern Spain.
In the algorithm comparison \textit{xgboost} showed the best performance among the tested ones.
Even though \ac{RR} is able to handle highly correlated data, it was far from achieving an acceptable performance in this work.

The fitted models on the plot level showed a promising performance with RMSE values between 8 and 20.
The performance of the model containing all data was acceptable (RMSE 29.59) but can be improved by adding more observations from other plots in future studies.

The spatial prediction showed a satisfying result making it possible to distinguish highly defoliated plots from plots with low defoliation easily.
The most important indices for the fitted model were widely known vegetations indices such as EVI, GDVI or NDVI.
It would be interesting to link the indices of this work to other indicators of forest/vegetation health in future studies and analyze their importance and the model performances.
In summary, defoliation can be successfully used as a response variable to model forest health using remote sensing indices.
